### 2023-08-30 appendixPN.tex
section

\problemx{zero-reachability}
{A $d$-reset-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$.} 
{  $\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$ ?\\}

@@

We describe therein how to "adjust" Theorem~5.5 in  \cite{peterson1981petri}, that shows that reachability can be reduced to liveness for Petri nets \cite{peterson1981petri}, reducing the {\em zero-reachability} problem to {\sc $t$-liveness} in reset Petri nets. \\

>>>>

\problemx{zero-reachability}
{A $d$-reset-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$.} 
{  $\exists q \in Q, ~ p(\textbf{u}) \to^* q(\textbf{0})$ ?\\}

@@

We will show that the {\em zero-reachability} problem can be reduced to {\sc $t$-liveness} in reset Petri nets; this is done by "adjusting" a similar result for Petri nets (Theorem~5.5 in  \cite{peterson1981petri}).\\

%that shows that reachability can be reduced to liveness for Petri nets \cite{peterson1981petri}, 
%reducing the {\em zero-reachability} problem to {\sc $t$-liveness} in reset Petri nets.
